### 2023-02-16 main.tex
Fixed
;;
fix
fixed
ll

\widehat{K}_{a}(x)=I+\frac{2x}{x+1}B_{L}

@@

K_{a}(x)=\left((2x+3)B_{1}+(x+3)I\right)\frac{1}{(x+1)^{2}(2x+3)}

@@

	K_{0}^{\Delta}=\left((2x+3)\widetilde{B}_{1}+(x+3)I\right)\frac{(1+x)^{2}(2x+3)}{(x+1)^{2}(2x+3)}=\begin{pmatrix}
		3+x&0&\ldots&0\\
		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\

@@

		(2x+3)(\alpha_{N}-\beta_{N})&0&\ldots&-x

@@

		3+x&0&\ldots&0\\
		(2x+3)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\

@@

(3+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+3)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=

@@

		A^{2L-1}=&2e_{11}^{tot}+\left(e_{11}^{tot}-\sum_{j=1\,:\,j\neq i}^{N}e_{jj}^{tot}\right)+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}

@@

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}
	\end{split}
\end{equation}

@@

\begin{align}
	Q_{2L+2}&=A^{2L+1}-D_{22}^{2L+1}-D_{33}^{2L+1}\\
	Q_{2L+1}&=2A^{2L+1}+A^{2L}-D_{22}^{2L}-D_{33}^{2L}\\
	Q_{2L}&=3A^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}-D_{33}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. 
\section{Conclusion}

>>>>

\widehat{K}_{a}(x)=I+\frac{2x}{(x+1)}B_{L}

@@

K_{a}(x)=\left((2x+N)B_{1}+(x+N)I\right)\frac{1}{(x+1)^{2}(2x+N)}

@@

	K_{0}^{\Delta}=\left((2x+N)\widetilde{B}_{1}+(x+N)I\right)\frac{(1+x)^{2}(2x+N)}{(x+1)^{2}(2x+N)}=\begin{pmatrix}
		N+x&0&\ldots&0\\
		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\

@@

		(2x+N)(\alpha_{N}-\beta_{N})&0&\ldots&-x

@@

		N+x&0&\ldots&0\\
		(2x+N)(\alpha_{2}-\beta_{2})&-x&\ldots&0\\

@@

(N+x)A(x)-\sum_{i=2}^{N}xD_{ii}(x)+\sum_{i=2}^{N}(2x+N)(\alpha_{i}-\beta_{i})B_{i}(x)\\&=

@@

		A^{2L-1}=&2e_{11}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)+2\sum_{a\neq b}e_{11}^{[a]}e_{11}^{[b]}

@@

\begin{equation}
	D_{ii}(x)=D_{ii}^{2L+1}x^{2L+1}+D_{ii}^{2L}x^{2L}+D_{ii}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficients
\begin{equation}\label{a2lp}
	D_{ii}^{2L+1}=-I^{tot}
\end{equation}\begin{equation}\label{a2l}
	D_{ii}^{2L}=I^{tot}-2e_{ii}^{tot}
\end{equation}
\begin{equation}\label{a2lm1}
	\begin{split}
		D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{a\neq b}e_{ii}^{[a]}e_{ii}^{[b]}-2\sum_{a\neq b}\sum_{j=2\,:\,j\neq i}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}-2\sum_{a\neq b}\sum_{j=2}^{N}e_{ij}^{[a]}e_{ji}^{[b]}\\
		&=e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}+2e_{ii}^{tot}\\
		&=2e_{11}^{tot}+2e_{ii}^{tot}-C_1
	\end{split}
\end{equation}

@@

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
	Q_{2L}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. 
\section{Conclusion}
